---
title: "Covid-19 in Switzerland"
author: "Marie Louise"
date: "`r date()`"
format: 
  html:
    toc: true
    toc-location: body 
    code-fold: show
    code-tools: true 
    df-print: paged
    embed-resources: true
  pdf: 
    toc: true
---

```{r}
#| output: false
#| label: Load Libraries

library(here)
library(tidyverse)
library(lubridate)
library(unibeCols)
```

## Introduction

The aim of this file is to evaluate **Covid-19** cases in Switzerland.

## Data

We read and process the cases as reported by the \[Federal Office of Public Health\] (https://idd.bag.admin.ch/).

```{r}
#| output: false 
#| label: Read data
cases <- read.csv(here("data/raw/COVID19Cases_geoRegion(2).csv"))
```


```{r}
# Process Data
region <- "CH"
window_start <- ymd("2020-09-01")
window_end <- ymd("2020-11-30")
cases <- cases |>
  filter(geoRegion == region & datum >= window_start & datum <= window_end) |>
  select(datum, entries)

```

@fig-cases shows the number of laboratory-confirmed cases of Covid-19 in CH from 

```{r}
#| label: fig-cases
#| fig-cap: "Laboratory-confirmed cases of Covid-19 in Switzerland in 2020"
#| fig-width: 8
#| fig-height: 4
#| dpi: 150
ggplot(cases, aes (x = datum, y = entries)) + 
  geom_bar(stat = "identity", fill = unibeSaphire()) + 
  labs(x ="Time", y = "Laboratory confirmed cases") + 
  theme_minimal()
```

## Conclusion

### Covid-19 in Switzerland
Here we write the summary aboud Covid-19 in general in CH.

### Period from 09/2020 to 11/2000
In this specific period... 


